---
title: "Science Fair"
author: "Tyler"
date: "September 18, 2016"
output: html_document
---

```{r setup, include=FALSE}
require(tigerstats)
```

# Introduction

In an effort to track the influence of direct sunlight on small structures with different surface coatings the following steps were taken. 

* seven toy houses were built of wood. Six different coatings were used and the bare wood house was named "control".  
* External temp of the coating on each test article was taken with an infrared thermometer in while the probe was placed in the structure and temp recorded after it stabelized ~ 30 seconds.  
* process was repeated hourly.  
* We want to investigate temperature differences across the different surface coatings


# Methods

We look at plots of temp readings over time.

```{r}
tempdata <- read.csv(file="comptonData.csv", header=TRUE)

df <- tempdata

for( i in 4:10 ) {
    df[i] <- df[i] - df[3] #normalize by outside temp
}
df$Day <- as.factor(df$Day) #correctly type day as factor
```

```{r}
xyplot(White ~ Time.Change | Day,
	data = df,
	layout = c(2,1),
	groups = thermo,
	auto.key = list(
		space = "top",
		title = "thermo",
		cex.title = 1,
		columns = 1),
	type = c("p","smooth"))
xyplot(White.with.Glass ~ Time.Change | Day,
	data = df,
	layout = c(2,1),
	groups = thermo,
	auto.key = list(
		space = "top",
		title = "thermo",
		cex.title = 1,
		columns = 1),
	type = c("p","smooth"))
xyplot(White.with.Zinc.Oxide ~ Time.Change | Day,
	data = df,
	layout = c(2,1),
	groups = thermo,
	auto.key = list(
		space = "top",
		title = "thermo",
		cex.title = 1,
		columns = 1),
	type = c("p","smooth"))

xyplot(Black ~ Time.Change | Day,
	data = df,
	layout = c(2,1),
	groups = thermo,
	auto.key = list(
		space = "top",
		title = "thermo",
		cex.title = 1,
		columns = 1),
	type = c("p","smooth"))
xyplot(Black.with.Glass ~ Time.Change | Day,
	data = df,
	layout = c(2,1),
	groups = thermo,
	auto.key = list(
		space = "top",
		title = "thermo",
		cex.title = 1,
		columns = 1),
	type = c("p","smooth"))
xyplot(Black.with.Zinc.Oxide ~ Time.Change | Day,
	data = df,
	layout = c(2,1),
	groups = thermo,
	auto.key = list(
		space = "top",
		title = "thermo",
		cex.title = 1,
		columns = 1),
	type = c("p","smooth"))
```
# Observations

##Black paint internal temps average higher than white painted ones.  

###can do with one way anova or ttest or wilcoxon  

##There is a larger average difference between black than white (surface to internal)
