---
title: "Science Fair"
author: "Tyler"
date: "September 18, 2016"
output: html_document
---

```{r setup, include=FALSE}
require(tigerstats)
```

# Introduction

In an effort to track the influence of direct sunlight on small structures with different surface coatings the following steps were taken. 

* seven toy houses were built of wood. Six different coatings were used and the bare wood house was named "control".  
* External temp of the coating on each test article was taken with an infrared thermometer in while the probe was placed in the structure and temp recorded after it stabelized ~ 30 seconds.  
* process was repeated hourly.  
* We want to investigate temperature differences across the different surface coatings


# Methods

We look at plots of temp readings over time.

```{r}
tempdata <- read.csv(file="comptonData.csv", header=TRUE)
xyplot(Outside ~ Time.Change | thermo,
	data = tempdata,
	layout = c(2,1),
	type = c("p","smooth"))

xyplot(White ~ Time.Change | thermo,
	data = tempdata,
	layout = c(2,1),
	type = c("p","smooth"))

xyplot(White.with.Glass ~ Time.Change | thermo,
	data = tempdata,
	layout = c(2,1),
	type = c("p","smooth"))

xyplot(White.with.Zinc.Oxide ~ Time.Change | thermo,
	data = tempdata,
	layout = c(2,1),
	type = c("p","smooth"))

xyplot(Black ~ Time.Change | thermo,
	data = tempdata,
	layout = c(2,1),
	type = c("p","smooth"))

xyplot(Black.with.Glass ~ Time.Change | thermo,
	data = tempdata,
	layout = c(2,1),
	type = c("p","smooth"))

xyplot(Black.with.Zinc.Oxide ~ Time.Change | thermo,
	data = tempdata,
	layout = c(2,1),
	type = c("p","smooth"))

```



## next look at each separately

You can also embed plots, for example:

```{r }
#subtract "outside" from all numeric temp colums using some variation of apply or dplyr then look at plots
```

